---
title: "Lasso"
author: "Kingsley Ofoegbu"
date: "4/19/2021"
output: pdf_document
---

```{r}
suppressMessages(library(tidyverse))
library(leaps)
library(glmnet)
library(MASS)
```


## load Data
```{r}
CovidData <- read_csv("./data/CovidDataSetFinal.csv")
CovidData = na.omit(CovidData)
attach(CovidData)
CovidData 
```

```{r}
n <- length(PercentWearingMask)
Z <- sample(n,n/2)
```

```{r}
reg <-
  lm(
    PercentWearingMask ~ Population + ApproximatePopulationDensity + cases + COVID_deaths + confirmed_cases + confirmed_deaths + PercentUnemployed + MedianHouseholdIncome + PercentAfricanAmerican + PercentHispanic + PercentAsianAmerican + PercentWhiteAmerican + PercentNativeAmericanAndAlaskaNative + PercentNativeHawaiianAndOtherPacificIslander + PercPeopleWithCollegeOrAssociateDegreePerYear + StatewideMaskRequirement + PercentMale + PercentFemale + PercAdultsWithLessThanHighSchoolDiploma + PercAdultsWithHighSchoolDiploma + PercAdultsWithSomeCollegeOrAssociateDegree + PercAdultsWithBachelorDegreeOrHigher,
    data = CovidData
  )
X <- model.matrix(reg)
summary(reg)
nrow(X)
```

```{r}
LassoCV1 <-
  cv.glmnet(X[Z, ],
            PercentWearingMask[Z],
            alpha = 1,
            lambda = seq(0, 10, 0.001))
LassoCV1$lambda.min
```
## Optimal Lambda
```{r}
LassoCV2 <- cv.glmnet(X[Z, ],
                     PercentWearingMask[Z],
                     alpha = 1,
                     lambda = seq(0, 0.1, 0.000001))
LassoCV2$lambda.min
```
### variables for lasso are Population, PercentUnemployed, MedianHouseholdIncome, PercentAfricanAmerican, PercentHispanic PercentNativeAmericanAndAlaskaNative, PercentNativeHawaiianAndOtherPacificIslander, StatewideMaskRequirement(yes), PercAdultsWithSomeCollegeOrAssociateDegree, PercAdultsWithBachelorDegreeOrHigher
```{r}
LASSO <- glmnet(X[Z,],
                PercentWearingMask[Z],
                alpha = 1,
                lambda = LassoCV2$lambda.min)
predict(LASSO, type = "coefficients")
```
```{r}
reg.fit <- regsubsets(
    PercentWearingMask ~ Population + ApproximatePopulationDensity + cases + COVID_deaths + confirmed_cases + confirmed_deaths + PercentUnemployed + MedianHouseholdIncome + PercentAfricanAmerican + PercentHispanic + PercentAsianAmerican + PercentWhiteAmerican + PercentNativeAmericanAndAlaskaNative + PercentNativeHawaiianAndOtherPacificIslander + PercPeopleWithCollegeOrAssociateDegreePerYear + StatewideMaskRequirement + PercentMale + PercentFemale + PercAdultsWithLessThanHighSchoolDiploma + PercAdultsWithHighSchoolDiploma + PercAdultsWithSomeCollegeOrAssociateDegree + PercAdultsWithBachelorDegreeOrHigher,
    data = CovidData
  )
summary(reg.fit)
```
```{r}
which.min( summary(reg.fit)$cp )

which.min( summary(reg.fit)$bic )

which.max( summary(reg.fit)$adjr2 )
```

